### 2010-03-25 docs/architecture/architecture.tex
describe some test problems

\item {\tt test\_basestate}
\item {\tt test\_diffusion}
\end{itemize}

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing the index space for which this \fab\ is defined
\item {\tt ibx} is a \boxtype\ that describes the index range of the valid data
  for the \fab.  This differes from {\tt bx} when the box is nodal in one more more 
  directions.
\item {\tt pbx} is a \boxtype\ that extends {\tt ibx} to include
  any ghostcells, or equivalently, the physical box for the \fab\
\item {\tt nc} is the number of components (how many variables at  
  each grid location)
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}

@@

The MAC velocities are allocated at each level of refinement,{\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)

@@

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic boxlib data types Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.

>>>>

\item {\tt test\_basestate} \\[-3mm]

  This test initializes the base state to contain a hydrostatic
  model and then evolves the state with heating to watch the 
  hydrostatic adjustment of the atmosphere.  In particular,
  the base state velocity, $w_0$, is computed in response to 
  the heating and this is used to advect the base state density
  and compute the new pressure, $p_0$.  An early version of 
  this routine was used for the plane-parallel expansion test
  in \cite{lowMach2}.  This version of the test was also shown
  for a spherical, self-gravitating star in \cite{multilevel}.

\item {\tt test\_diffusion}

  This test initializes a Gaussian temperature profile and calls
  the thermal diffusion routines in MAESTRO to evolve the state 
  considering only diffusion.  The driver estimates a timestep
  based on the explicit thermal diffusion timescale and loops
  over calls to the thermal diffusion solver.  A Gaussian remains
  Gaussian when diffusing, so an explicit error can be computed
  by comparing to the analytic solution.  This test is 
  described in \cite{xrb}.

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing the index space for which this \fab\ is defined
\item {\tt ibx} is a \boxtype\ that describes the index range of the valid data
  for the \fab.  This differes from {\tt bx} when the box is nodal in one or more 
  directions.
\item {\tt pbx} is a \boxtype\ that extends {\tt ibx} to include
  any ghostcells, or equivalently, the physical box for the \fab\
\item {\tt nc} is the number of components (how many variables at  
  each grid location)
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}

@@

The MAC velocities are allocated at each level of refinement, {\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)

@@

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic boxlib data types. Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.
